Multimodal Corpora

### 2017-01-03 paper.tex
Fertsch

				\begin{table}
					\center
					\begin{tabular}{|l|c|}
						\hline 
						\textbf{Specification} & \textbf{Value} \\ 
						\hline 
						Number of dialogs & 25 \\ 
						\hline 
						Video time & 280 minutes \\ 
						\hline 
						Video specification & 720x576, 25fps  \\ 
						\hline 
						Video codec & H.264  \\ 
						\hline 
						Video feeds & 3 \\ 
						\hline 
						Audio feeds & 1 \\ 
						\hline
					\end{tabular} 
					\caption{Primary data of the \gls{saga} corpus}
					\label{table:sagaPrimary}
				\end{table}

			\subsubsection{Secondary Data}
				The secondary data of the corpus contains on the one hand the annotation of the speech and on the other hand the annotation of the gestures. The speech annotation transcribes the utterance on the level of words. Furthermore the utterance is grouped in clauses, each containing a communicative goal \cite[ch. 2]{Bielefeld2010}:
				\begin{itemize}
					\item Naming a landmark
					\item Landmark property description
					\item Landmark construction description
					\item Landmark position description
				\end{itemize}

@@

				\begin{table}
					\center
					\begin{tabular}{|l|c|}
						\hline
						\textbf{Specification} & \textbf{Value} \\ 
						\hline 
						Words & 39,435 \\ 
						\hline 
						Iconic/Deictic gestures & 4961 \\ 
						\hline 
						Discourse gestures & approx. 1000 \\ 
						\hline 
					\end{tabular} 
					\caption{Secondary data of the \gls{saga} corpus}
				\label{table:sagaSecondary}
				\end{table}

		\subsection{Application}

>>>>

				\begin{table}
					\center
					\begin{tabular}{|l|c|}
						\hline 
						\textbf{Specification} & \textbf{Value} \\ 
						\hline 
						Number of dialogs & 25 \\ 
						\hline 
						Video time & 280 minutes \\ 
						\hline 
						Video specification & 720x576, 25fps  \\ 
						\hline 
						Video codec & H.264  \\ 
						\hline 
						Video feeds & 3 \\ 
						\hline 
						Audio feeds & 1 \\ 
						\hline
					\end{tabular} 
					\caption{Primary data of the \gls{saga} corpus \cite{Bielefeld2010, BAS2014}}
					\label{table:sagaPrimary}
				\end{table}

			\subsubsection{Secondary Data}
				The secondary data of the corpus (\ref{table:sagaSecondary}) contains on the one hand the annotation of the speech and on the other hand the annotation of the gestures. The speech annotation transcribes the utterance on the level of words. Furthermore the utterance is grouped in clauses, each containing a communicative goal \cite[ch. 2]{Bielefeld2010}:
				\begin{itemize}
					\item Naming a landmark
					\item Landmark property description
					\item Landmark construction description
					\item Landmark position description
				\end{itemize}

@@

				\begin{table}
					\center
					\begin{tabular}{|l|c|}
						\hline
						\textbf{Specification} & \textbf{Value} \\ 
						\hline 
						Words & 39,435 \\ 
						\hline 
						Iconic/Deictic gestures & 4961 \\ 
						\hline 
						Discourse gestures & approx. 1000 \\ 
						\hline 
					\end{tabular} 
					\caption{Secondary data of the \gls{saga} corpus \cite{Bielefeld2010}}
				\label{table:sagaSecondary}
				\end{table}

		\subsection{Application}
			The authors of the \gls{saga} corpus present two different applications in \cite[ch. 4]{Bielefeld2010}.

			The first application is to create a \textbf{typological grid} based on the morphological gesture annotation. The aim of this application was to determine whether the shapes arising from the gestures are systematically used or if they are arbitrary tokens. Furthermore it has to be investigated if this systematic usage is only observed in one dialog, by only one participant or even in the whole corpus. With this additional information about the gestures, forming the connection between the meaning of the spoken language and the gestures can be simplified. The typology provides a more high level way of classifying gestures and gesture sequences. The findings of this research was published in \cite{Hahn2010}.

			The second usage of the corpus involves the automatic generation of iconic gestures for virtual Avatars. To do this the \gls{saga} corpus was used to learn \textbf{bayesian networks}. This networks can also be used to compare the gesture production of two individuals. The different propability distributions of the networks enable novel insights in the gesture generation process \cite[ch. 4.2]{Bielefeld2010}.
